### 2019-12-26 article.tex
one limitation added
some future directions added

>>>>

Our approach has some bias as the whole dataset was obtained from one center and was pre-processed together in the beginning. To resolve this issue, we can try to examine the proposed method on a bigger dataset consisted of different scans obtained using different instruments. Also, we can include other diseases (such as Alzheimer and Schizophrenia) patients as healthy control, to see how the proposed method will do the job.

To improve this method, we can try to investigate more on data and results to tune dropout probabilities and detection threshold (line~\ref{alg:proposedMethod:threshold} of Algorithm \ref{alg:proposedMethod}). In addition to that, we can try to employ competitor neural networks such as GoogleNet and try to utilize them using Bayesian methods in the task of Parkinson's disease diagnosis. Furthermore, we will be able to compare the proposed method to other rivals and improve this model.

In this study, we showed that spatial information is powerful enough to diagnose Parkinson's disease. Moreover, we can try to implement a hybrid solution based on the proposed method that uses temporal connectivities as well. For instance, we can use functional connectivity based algorithms \cite{Rashid2016} \cite{Shen2014} \cite{Calhoun2004} \cite{GonzalezCastillo2015} \cite{Greicius2002} \cite{Arribas2010} \cite{Leonardi2013} \cite{Liu2015} \cite{Liu2016} \cite{Lehmann2017} or statistical/Bayesian based methods \cite{HanchuanPeng2005} \cite{Flandin2007} \cite{Ahmad2016} \cite{Power2012} \cite{Oikonomou2010} \cite{GomezLaberge2011} \cite{Zhang2001} \cite{Oikonomou2012} \cite{Oikonomou2013} \cite{Younes2006} \cite{Calhoun2012}. Ensembling can be done by training mentioned methods combined with Bayesian units or by adding their extracted features to the existing network.
